\subsection{Darfur is Dying Quiz}\subsubsection{When did the violence in Darfur first start?} \begin{enumerate} \item 2001 \item 2002 \item 2003 \item 2004 \item 2005\end{enumerate}\subsubsection{Who is the fighting between?} \begin{enumerate} \item two different tribes \item arabs and non-arabs \item Hutu and Tutsi \item Blacks and Whites \item rich and poor\end{enumerate}\subsubsection{A genocide is defined as killing, causing serious bodily or mental harm and preventing births of ...} \begin{enumerate} \item a specific national group \item a specific ethnical group \item a specific racial group \item a specific religious group \item all of the above\end{enumerate}\subsubsection{How did the conflict start?} \begin{enumerate} \item bombing in a main city \item government's drafting of soldiers \item accidental killing of 5 civilians by police \item rebellion attacks of government targets \item public protest against new law\end{enumerate}\subsubsection{How many people have died as a result of the violence, hunger, and disease?} \begin{enumerate} \item up to 3,000 \item up to 30,000 \item up to 300,000 \item up to 3,000,000 \item up to 3.5 milion\end{enumerate}\subsubsection{Where is Darfur?} \begin{enumerate} \item northern Sudan \item southern Sudan \item eastern Sudan \item western Sudan \item central Sudan\end{enumerate}\subsubsection{When was the height of the violence in Darfur?} \begin{enumerate} \item 2003-2004 \item 2003-2005 \item 2004-2005 \item 2004-2006 \item 2005-2006\end{enumerate}\subsubsection{What group is referred to as Devils on horseback?} \begin{enumerate} \item Sunnis \item Shiite \item Tumoils \item Janjaweed\end{enumerate}\subsubsection{Darfur is a region in the African country of Sudan. Which countries border Sudan?} \begin{enumerate} \item Rwanda, Somalia, Tanzania \item Algeria, Morocco, Tunisia \item Central African Republic, Chad, Libya \item Kenya, Ethiopia, Malawi\end{enumerate}\subsubsection{ Which two major powers united with the Sudanese government to keep the United Nations out of Darfur?} \begin{enumerate} \item United States and Canada \item Iraq and Iran \item Egypt and Libya \item Russia and China\end{enumerate}