\subsection{The Oregon Trail Quiz}\subsubsection{How many miles long was the Oregon Trail?} \begin{enumerate} \item 500 Miles \item 1000 Miles \item 2000 Miles \item 3000 Miles \item 20000 Miles\end{enumerate}\subsubsection{What is the name of a disease like malaria that the pioneers might catch?} \begin{enumerate} \item ague \item pneumonia \item epilepsy \item measles\end{enumerate}\subsubsection{What year was the first Oregon Trail wagon train organized?} \begin{enumerate} \item 1847 \item 1843 \item 1899 \item 1876 \item 1836\end{enumerate}\subsubsection{What disease killed more people on the trail than any other?} \begin{enumerate} \item smallpox \item plague \item cholera \item scarlet fever\end{enumerate}\subsubsection{When was the first transcontinental railroad finished that eventually ended the Oregon Trail?} \begin{enumerate} \item 1867 \item 1870 \item 1899 \item 1869\end{enumerate}\subsubsection{How many modern states did the travelers travel through when crossing the trail?} \begin{enumerate} \item 6 \item 8 \item 3 \item 10\end{enumerate}\subsubsection{How many people died on the Oregon Trail?} \begin{enumerate} \item 50,000-60,000 \item 20,000-30,000 \item 90,000-100,000 \item 10,000-20,000\end{enumerate}\subsubsection{Where did the Oregon Trail begin?} \begin{enumerate} \item Independence, Mississippi \item Independence, Missouri \item Independence, Michigan \item Independence, Montana \item Independence, Massachusetts\end{enumerate}\subsubsection{Where did the Oregon Trail end?} \begin{enumerate} \item Vancouver, Washington \item The Dalles, Oregon \item Portland, Oregon \item Stevenson, Washington \item Oregon City, Oregon\end{enumerate}\subsubsection{How many people came west on the Oregon Trail?} \begin{enumerate} \item around 500 \item around 5000 \item around 50000 \item around 500000 \item around 5000000\end{enumerate}