\section{Location of Game Encyclopedia}{Some educational games include a game encyclopedia as part of the game, either internally or externally as a game manual or wiki. Having such an encyclopedia available within the game greatly increases the chance of players using it for self-directed and self-motivated learning, as part of tangential learning.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Game contains no encyclopedia of game content}\paragraph{2}{Game information is located online, in a non-central location}\paragraph{3}{Game has an outside manual (or wiki) of game content}\paragraph{4}{Game doesn't have an in-game encyclopedia, but points to a central location elsewhere}\paragraph{5}{Game has an in-game encyclopedia of game content}\paragraph{Examples}Examples of games with an encyclopedia with a good location include the Civilization series (for their Civilopedia) and the Total War series. Both of these games contain an in-game encyclopedia that players can access with one click. \section{Content of Game Encyclopedia}{Having a game encyclopedia as part of the game encourages self-motivated players to seek out additional help. If the encyclopedia includes more than just game mechanics as part of its content, players may be more encouraged to self-educate themselves about those topics.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Game contains no encyclopedia or Encyclopedia contains no content}\paragraph{2}{Encyclopedia contains content only related to game mechanics}\paragraph{3}{Encyclopedia contains information about game mechanics, and also limited historical/factual information}\paragraph{4}{Encyclopedia contains content related to game mechanics and historical/factual information}\paragraph{5}{Encyclopedia contains content related to game mechanics and historical/factual information and outside links or references}\paragraph{Examples}Examples of games with an encyclopedia that contains both mechanics and historical/factual information include Civilization and the Total War series, as well as most historical simulation games. All of these games' encyclopedias contain copious amounts of game mechanics information, as well as historical and factual information about each item in the game.\section{Amount of Referential Material}{By having many objects or events in the game that are references to real-life objects or events, players may recognize certain objects or events and self-motivate themselves to learn more about those objects or events. More objects like that in the game means more chances for a player to recognize a real-life object or event.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{No game objects or events are references to real-life objects or events}\paragraph{2}{At least one event or object is a reference to a real-world event or object}\paragraph{3}{Several non-connected events or objects are references to a real-world event or object}\paragraph{4}{At least one group of objects or events are references to real-life objects or events}\paragraph{5}{Numerous groups of objects or events are references to real-life objects or events}\paragraph{Examples}The Oregon Trail is a game with huge amounts of referential material; just about every item and event in the game is historically accurate.\section{Popularity of Referential Material}{Having real-life objects or events in the game means that some players will recognize them and attempt to self-educate themselves about those objects or events. In addition, having a large amount of those references be popular means that more players will recognize the more popular objects/events, and by association, education about the lesser-known objects/events will be the result of self-motivated education about the popular items.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Existing references are extremely obscure}\paragraph{2}{Some of the references are popular}\paragraph{3}{About half of the references are popular}\paragraph{4}{Many of the references are popular}\paragraph{5}{Most or all of the references are popular}\paragraph{Examples}Where in the World is Carmen Sandiego is a game with many popular references. In contrast to The Oregon Trail, where all of the content is specific to that time period and may be totally unfamiliar to players, Carmen Sandiego's wide range of concepts (geography, landmarks, cultures, religions, etc) is likely to be recognized by many different players.\section{Rewards for knowing Referential Material}{If games allow players to use their knowledge of the referential material in a positive manner within the game, it reinforces the desire for the player to tangentially learn about all the referential material in the game. This is in contrast to traditional methods, where the content that the player is trying to be educated about serves as a barrier of entry to the later levels of the game, or the game penalizes players that don't know the content; with this, players can still play the entirety of the game, but are incentivized to do better by learning the referential material.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Knowing the referential material is purely irrelevant; doesn't affect the gameplay at all}\paragraph{2}{Knowing the referential material is a little useful; only affects the gameplay a small amount}\paragraph{3}{Knowing the referential material is somewhat useful; moderately affects the player's choices during gameplay}\paragraph{4}{Knowing the referential material is very useful; usually affects the player's choices}\paragraph{5}{Knowing the referential material always significantly affects gameplay}\paragraph{Examples}In Kerbal Space Program, players aren't taught about aerodynamics, power-to-weight ratios, or how to transfer orbits. However, if they do know and understand that material, building, launching, and maneuvering an orbital craft becomes much easier.\section{Adaptive Difficulty}{In order to incorporate flow as much as possible, the game must use a form of Adaptive Difficulty; the game tries to match the difficulty of the obstacles to the skill level of the player. This can be done in a rudimentary way by allowing the player to select the difficulty themselves, but is most effective when it recognizes how well a player is doing on a certain puzzle and adjusting the difficulty automatically. This ensures that the player isn't trivially challenged, but at the same time isn't pushed outside the bounds of their ability.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Game only has one difficulty}\paragraph{2}{Game has several difficulties, but players can only select difficulty at beginning of game}\paragraph{3}{Game has several difficulties, and players can change difficulty mid-game}\paragraph{4}{Game has several difficulties, and prompts the player to increase or decrease the difficulty as needed}\paragraph{5}{Game has several difficulties, and automatically adjusts the difficulty of the game as needed}\paragraph{Examples}In The Logical Journey of the Zoombinis, players must complete challenges with 16 zoombinis. If the player passes the level, they continue with all their Zoombinis. If the player does poorly on the level, they can still pass the level; they just lose Zoombinis depending on how poorly they did. A lost zoombini returns to the previous checkpoint (spaced every 3 levels), and players can only embark from a checkpoint with 16 Zoombinis. If the player has a 100% success rate on the level, the level's difficulty increases, so that the next time the player plays the level they must either have a 100% success rate or lose a Zoombini, so that they must complete the level at the same difficulty again later.\section{Contextual Tutorials}{In keeping with flow, players need to be challenged at their level of skill within every game. This means that players shouldn't be hindered by challenges that are too easy for them, but likewise shouldn't feel completely lost on difficult challenges. The method of introducing these challenges is equally important; players that are forced to go through numerous, easy introductory levels will quickly become bored, but players that skip through tutorials at later stages or forget about valuable information learned early in the game quickly become frustrated. It's important to give the player only information that they need; similar to the concept of adaptive difficulty, the game gives the player helpful hints or suggestions when they are stuck, or when the player doesn't intuitively grasp a new mechanic the first time. Similarly, there needs to be tutorials for just about every concept in the game, to cater to players that might have learning 'gaps' in their history.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Tutorials aren't given in the game}\paragraph{2}{Tutorials are given at the beginning of the game}\paragraph{3}{Tutorials are given every few levels/sections of the game}\paragraph{4}{Tutorials are given at the beginning of every level/section}\paragraph{5}{Tutorials are offered continuously}\paragraph{Examples}In The Oregon Trail, players are offered to 'ask someone for advice' every time that they have to stop. This means that experienced players aren't bothered by tutorials that they've seen before, and that newer players can stay confident that help is available if they need it.\section{Low game resource penalty for failure}{In order for the game to encourage exploration and play, the player needs to feel free to fail. This means that if the player does fail, there is a minimal amount of game resources (e.g. lives, tries, health points) consumed each time the player fails. With this, the player is comfortable trying different solutions to problems within the game without much penalty.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Game resource penalty is extreme (e.g. restart the game)}\paragraph{2}{Game resource penalty is large (e.g. 1/3 lives, 10 health points / 100)}\paragraph{3}{Game resource penalty is moderate}\paragraph{4}{Game resrouce penalty is small}\paragraph{5}{Game resource penalty is nonexistent (e.g. unlimited lives)}\paragraph{Examples}Light Bot and BotLogic are great examples of minimal resource penalties. Instead of having 3 tries to solve a level before reverting to a previous level, players can restart the level at any time, keeping their progress. In contrast, Number Munchers' resource penalty is very large; every time the player fails, they lose one of their three lives.\section{Low "reset time" for failure (time to return to failure point)}{In order for the game to encourage exploration and play, the player needs to feel free to fail. This means that if the player does fail, there is a minimal amount of external resources (e.g. time, frustration) consumed each time the player fails. With this, the player is comfortable trying different solutions to problems within the game without much penalty. }\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Reset time is very long (e.g. reloading level takes a long time)}\paragraph{2}{Reset time is long (e.g. greater than 10 seconds)}\paragraph{3}{Reset time is moderate (e.g. up to 10 seconds)}\paragraph{4}{Reset time is short (e.g. a few seconds)}\paragraph{5}{Reset time is very short (e.g. near instant)}\paragraph{Examples}Light Bot and BotLogic are great examples of minimal reset penalties. Instead of having to wait several seconds while the level is reloaded after a failure, players are instantly reset. Games that score poorly on this are characterized by long load and setup times.\section{High checkpoint frequency}{It's important to have players feel free to fail within games. Having a high frequency of checkpoints reduces both the amount of time/frustration that it takes for the player to return to the point of a failure, as well as in-game resources.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Zero checkpoints}\paragraph{2}{Checkpoints are few and far between (e.g. levels are the only places to restart)}\paragraph{3}{Checkpoints are moderate}\paragraph{4}{Checkpoints are numerous (e.g. players can restart at the beginning of each puzzle)}\paragraph{5}{Checkpoints are frequent (e.g. players can restart part of the way through puzzles)}\paragraph{Examples}Light Bot and BotLogic have excellent checkpoints, represented by each level. In contrast, The Logical Journey of the Zoombinis has poor checkpoints, due to their appearance only every few levels.\section{Freedom of exploration}{If players are to be encouraged to explore, the nature of the game must be nonlinear and allow for players to progress in varying sections of the game at their own pace. That isn't saying that they shouldn't have a finite goal to work towards, but the methods or paths with which they work towards that goal should be optional and variable.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Players are placed in a strictly linear world or lesson progression}\paragraph{2}{Players are allowed just a few large-scale choices in their game world}\paragraph{3}{Players have the option to make choices about the direction of their progression in the world, but it is largely linear}\paragraph{4}{Players can choose from many choices within the game world to explore, including lessons}\paragraph{5}{Players are free to choose the direction they want, both educationally and within the game world; allowed to jump between parallel lessons}\paragraph{Examples}Pandemic 2 is a great example of a game with a high degree of freedom of exploration. Players can choose the methods and targets they use in the game world with little repercussion. By using completely different play styles each session, they can observe the choices of their actions and gain insight as to how the game world works.\section{Iterative feedback}{In the case of games with a high degree of free-form exploration, it's easy to see that some players might get lost and become frustrated. In order to maintain flow, these players must receive some kind of feedback that they're on the right track, and not just wandering aimlessly through the game world or puzzles. It's extremely helpful for players to receive feedback at every step they take, even during the completion of puzzles; that way, they can be sure that they're progressing, and easily see the steps ahead of them, enabling flow.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{Game gives no feedback other than high-level progression through the game}\paragraph{2}{Game gives feedback after each level}\paragraph{3}{Game gives feedback at various points through a level, after a series of puzzles}\paragraph{4}{Game gives feedback after each puzzle}\paragraph{5}{Game constantly gives feedback (e.g. during a puzzle)}\paragraph{Examples}The Incredible Machine gives pretty good feedback during each puzzle; it's easy for players to see how close they came to achieving their goals (e.g. `the ball got closer to the basket that time'). \section{Unorthodox problem solving}{Another important element of allowing players to explore and play is to give them the option to solve problems using unorthodox solutions; solutions that the game didn't anticipate, but still validate the puzzle's end condition. Sometimes, the player may be able to figure out how to circumvent certain sections of a puzzle; this should still be considered valid, but it's hoped that the circumvention wasn't because of faulty game logic. This allows players to try unusual solutions to problems, and help them understand the system far better than if they had just been taught the correct solution.}\paragraph{}The rubric to measure the quality of how a game satisfies this attribute is as follows.\paragraph{1}{There is only one way to solve any given problem, with one given progression that is valid as a solution}\paragraph{2}{Some problems within the game may be solved more than one way}\paragraph{3}{Multiple solutions are available for each problem, but players are limited to using one of those solutions}\paragraph{4}{Players can solve each problem via any solution, so long as they do not circumvent it}\paragraph{5}{Players can solve a problem any way they like, or even circumvent the problem, and be given full (or bonus) points}\paragraph{Examples}Lemmings is a perfect example of unorthodox problem solving. Players can solve any level any way they like, so long as they get the requisite number of Lemmings to the exit. Players can tell the Lemmings to dig, build, climb, or fall any way that they think will help them get to the exit, even if it's not what the original designers intended.