\subsection{Basic Survey}\subsubsection{What is your gender?}\begin{itemize} \item Male \item Female \end{itemize}\subsubsection{What is your age?} (An empty text box where workers can only enter numbers) \subsubsection{How many years have you been playing video games?} (An empty text box where workers can only enter numbers) \subsubsection{Fun games can be educational.}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Most fun games are educational.}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Games are more fun when they are cooperative (instead of competitive).}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Games are more fun when you play by yourself (instead of with others).}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Games are more fun when you play online (instead of with others in the same room).}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Educational games can be fun.}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Most educational games are fun.}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Games are more educational when they are cooperative (instead of competitive).}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Games are more educational when you play by yourself (instead of with others).}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{Games are more educational when you play online (instead of with others in the same room).}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{List some fun games.} (An empty text box where workers can write anything) \subsubsection{List some educational games.} (An empty text box where workers can write anything) \subsection{Rubric}\subsubsection{Does this game have an encyclopedia of game content? If so, where?} \begin{enumerate} \item Game contains no encyclopedia of game content \item Game information is located online, in a non-central location \item Game has an outside manual (or wiki) of game content \item Game doesn't have an in-game encyclopedia, but points to a central location elsewhere \item Game has an in-game encyclopedia of game content\end{enumerate}\subsubsection{If this game contains an encyclopedia of game content, what kind of content does it contain?} \begin{enumerate} \item Game contains no encyclopedia or Encyclopedia contains no content \item Encyclopedia contains content only related to game mechanics \item Encyclopedia contains information about game mechanics, and also limited historical/factual information \item Encyclopedia contains content related to game mechanics and historical/factual information \item Encyclopedia contains content related to game mechanics and historical/factual information and outside links or references\end{enumerate}\subsubsection{How many game objects or events reference real-life objects or events?} \begin{enumerate} \item No game objects or events are references to real-life objects or events \item At least one event or object is a reference to a real-world event or object \item Several non-connected events or objects are references to a real-world event or object \item At least one group of objects or events are references to real-life objects or events \item Numerous groups of objects or events are references to real-life objects or events\end{enumerate}\subsubsection{Of the objects/events that are in the game, how recognizable/popular are they?} \begin{enumerate} \item Existing references are extremely obscure \item Some of the references are popular \item About half of the references are popular \item Many of the references are popular \item Most or all of the references are popular\end{enumerate}\subsubsection{How much does knowing the real-life objects/events affect the gameplay?} \begin{enumerate} \item Knowing the referential material is purely irrelevant; doesn't affect the gameplay at all \item Knowing the referential material is a little useful; only affects the gameplay a small amount \item Knowing the referential material is somewhat useful; moderately affects the player's choices during gameplay \item Knowing the referential material is very useful; usually affects the player's choices \item Knowing the referential material always significantly affects gameplay\end{enumerate}\subsubsection{How many difficulty levels are there in the game, and how is the difficulty changed?} \begin{enumerate} \item Game only has one difficulty \item Game has several difficulties, but players can only select difficulty at beginning of game \item Game has several difficulties, and players can change difficulty mid-game \item Game has several difficulties, and prompts the player to increase or decrease the difficulty as needed \item Game has several difficulties, and automatically adjusts the difficulty of the game as needed\end{enumerate}\subsubsection{How often are tutorials offered in the game?} \begin{enumerate} \item Tutorials aren't given in the game \item Tutorials are given at the beginning of the game \item Tutorials are given every few levels/sections of the game \item Tutorials are given at the beginning of every level/section \item Tutorials are offered continuously\end{enumerate}\subsubsection{If the player fails, how many game resources do they lose?} \begin{enumerate} \item Game resource penalty is extreme (e.g. restart the game) \item Game resource penalty is large (e.g. 1/3 lives, 10 health points / 100) \item Game resource penalty is moderate \item Game resrouce penalty is small \item Game resource penalty is nonexistent (e.g. unlimited lives)\end{enumerate}\subsubsection{If the player fails, how long is the wait until they restart play?} \begin{enumerate} \item Reset time is very long (e.g. reloading level takes a long time) \item Reset time is long (e.g. greater than 10 seconds) \item Reset time is moderate (e.g. up to 10 seconds) \item Reset time is short (e.g. a few seconds) \item Reset time is very short (e.g. near instant)\end{enumerate}\subsubsection{How often are there in-game checkpoints?} \begin{enumerate} \item Zero checkpoints \item Checkpoints are few and far between (e.g. levels are the only places to restart) \item Checkpoints are moderate \item Checkpoints are numerous (e.g. players can restart at the beginning of each puzzle) \item Checkpoints are frequent (e.g. players can restart part of the way through puzzles)\end{enumerate}\subsubsection{How much freedom of choice is there in the game, including both game world and choice of lessons?} \begin{enumerate} \item Players are placed in a strictly linear world or lesson progression \item Players are allowed just a few large-scale choices in their game world \item Players have the option to make choices about the direction of their progression in the world, but it is largely linear \item Players can choose from many choices within the game world to explore, including lessons \item Players are free to choose the direction they want, both educationally and within the game world; allowed to jump between parallel lessons\end{enumerate}\subsubsection{How much and how often is there feedback regarding progress on the game?} \begin{enumerate} \item Game gives no feedback other than high-level progression through the game \item Game gives feedback after each level \item Game gives feedback at various points through a level, after a series of puzzles \item Game gives feedback after each puzzle \item Game constantly gives feedback (e.g. during a puzzle)\end{enumerate}\subsubsection{Are problems able to be solved multiple ways, or circumvented entirely?} \begin{enumerate} \item There is only one way to solve any given problem, with one given progression that is valid as a solution \item Some problems within the game may be solved more than one way \item Multiple solutions are available for each problem, but players are limited to using one of those solutions \item Players can solve each problem via any solution, so long as they do not circumvent it \item Players can solve a problem any way they like, or even circumvent the problem, and be given full (or bonus) points\end{enumerate}\subsubsection{This game was fun.}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{I had fun playing this game.}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{This game was educational.}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{I learned something from playing this game.}\begin{itemize} \item Strongly Agree \item Agree \item Disagree \item Strongly Disagree \end{itemize}\subsubsection{What did you learn from playing this game?} (An empty text box where workers can write anything) \subsubsection{Provide some comments and feedback on the game.} (An empty text box where workers can write anything) \subsubsection{Provide some comments and feedback on this survey.} (An empty text box where workers can write anything) \subsubsection{Estimate the number of minutes that you've played this game.} (An empty text box where workers can only enter numbers) \subsubsection{Estimate your highest score/level from your play session.} (An empty text box where workers can only enter numbers) 